A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-08-17 01_TrialsForInclusionInAnalysis.Rmd
Editing and formating

Studies were collated from the following locations and years and were considered for inclusion in this analysis.

* 2001  
   + Bongeen #1  
   + Bongeen #2

* 2002  
   + Hermitage #1  
   + Hermitage #2  
   + Kingaroy

* 2004  
   + Redvale

* 2010  
   + Hermitage  
   + Kingaroy

* 2011  
   + Hermitage  
   + Kingaroy

* 2012  
   + Gatton  
   + Kingaroy

* 2013  
   + Premer  
   + Millmerran   
   + Marys Mount  
   + Goolhi

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due to insufficient/late disease infection  
   + Emerald

* 2016  
   + Hermitage  
   + Kingaroy  
   + Emerald

* 2017  
   + Missen Flats (Fogerty's farm)  
   + Hermitage

* 2018  
   + Wellcamp

* 2019  
   + Hermitage

## Experiment locations

@@

## Import data and apply selection criteria

### Import data from trials we have the raw data  
```{r import_dataRAW}
PM_MB_raw <- 
   rbind(
      read.csv(here("cache/2010 PMmung Hermitage means.csv"), stringsAsFactors = FALSE),
      read.csv(here("cache/2011 PMmung Herm means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/2011 PMmung Kingaroy means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/AM1305_Goolhi_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/AM1304-MarysMount_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/AM1303-Premer-Disease_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/BB1305_Millmerran_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Herm_16_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/King_16_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Fogerty_17_mean.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Hermitage_17_mean.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Wellcamp_18_mean.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Hermitage_19_mean.csv"),stringsAsFactors = FALSE)
      )
write.csv(PM_MB_raw, file = here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"), row.names = FALSE)
```

@@

PM_MB_dat <- PM_MB_dat %>%
   filter(!is.na(grain_yield.t.ha.))
```
One more trial removed as it did not report disease severity.  
```{r TrialsWithotDisease}
PM_MB_dat %>%
   filter(is.na(PM_final_severity)) %>%
   distinct(trial_ref, year, location)

@@

No trials from our subset need to be removed for not reporting fungicide application dates.  
```{r FungicideApplicationDates}
PM_MB_dat %>%
   group_by(trial_ref) %>%
   summarise(No_Record_Of_Fungicide_Application_Dates = all(is.na(fungicide_application_1)),
             .groups = 'drop')%>%
   filter(No_Record_Of_Fungicide_Application_Dates)
```
No trials from our subset need to be removed for not reporting fungicide dose.  
```{r FungicideDoseTrials}
PM_MB_dat %>%
   group_by(trial_ref) %>%
   summarise(No_Record_Of_Fungicide_Dose = all(is.na(dose_ai.ha)),
             .groups = 'drop')%>%
   filter(No_Record_Of_Fungicide_Dose)
```

@@

We need to focus the meta-analysis on fungicides with the same mode of action.
Let's look at all the fungicides and retain the best represented fungicide group in the data.
```{r Fungicides}
PM_MB_dat %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise(groups = 'drop') %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   coord_flip()
```
The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.

@@

We will retain the trials trials which only contain DMI fungicides.  
```{r}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
```
We will retain all fungicides for now and remove them before the analysis.

>>>>

<br>
<br>
<br>

<br>
<br>
<br>

## Import data and apply selection criteria  
### Import data from trials we have the raw data  
```{r import_dataRAW}
PM_MB_raw <- 
   rbind(
      read.csv(here("cache/2010 PMmung Hermitage means.csv"), stringsAsFactors = FALSE),
      read.csv(here("cache/2011 PMmung Herm means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/2011 PMmung Kingaroy means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/AM1305_Goolhi_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/AM1304-MarysMount_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/AM1303-Premer-Disease_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/BB1305_Millmerran_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Herm_16_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/King_16_means.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Fogerty_17_mean.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Hermitage_17_mean.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Wellcamp_18_mean.csv"),stringsAsFactors = FALSE),
      read.csv(here("cache/Hermitage_19_mean.csv"),stringsAsFactors = FALSE)
      )
write.csv(PM_MB_raw, file = here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"), row.names = FALSE)
```

<br>
<br>
<br>

<br>
<br>
<br>

<br>

### Experiment locations

@@

<br>
<br>
<br>

## Subset data to selection criteria

@@

PM_MB_dat <- PM_MB_dat %>%
   filter(!is.na(grain_yield.t.ha.))
```

<br>
<br>
<br>

One more trial removed as it did not report disease severity.  
```{r TrialsWithotDisease}
PM_MB_dat %>%
   filter(is.na(PM_final_severity)) %>%
   distinct(trial_ref, year, location)

@@

<br>
<br>
<br>

No trials from our subset need to be removed for not reporting fungicide application dates.  
```{r FungicideApplicationDates}
PM_MB_dat %>%
   group_by(trial_ref) %>%
   summarise(No_Record_Of_Fungicide_Application_Dates = all(is.na(fungicide_application_1)),
             .groups = 'drop')%>%
   filter(No_Record_Of_Fungicide_Application_Dates)
```

<br>
<br>
<br>

No trials from our subset need to be removed for not reporting fungicide dose.  
```{r FungicideDoseTrials}
PM_MB_dat %>%
   group_by(trial_ref) %>%
   summarise(No_Record_Of_Fungicide_Dose = all(is.na(dose_ai.ha)),
             .groups = 'drop')%>%
   filter(No_Record_Of_Fungicide_Dose)
```

<br>
<br>
<br>

@@

<br>
<br>
<br>

We need to focus the meta-analysis on fungicides with the same mode of action.
Let's look at all the fungicides and retain the best represented fungicide group in the data.
```{r Fungicides}
PM_MB_dat %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise(groups = 'drop') %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   coord_flip()
```

The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
Thee DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.

@@

<br>
<br>
<br>

We will retain the follow trials which only contain DMI fungicides. 
However we won't remove non-DMI fungicides just yet, we will do this before the analysis. 
```{r}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
```

<br>
<br>
<br>
<br>

### Classify dataset variables
